|

### 2021-11-11 article/article.Rmd
submission 2nd attempt

---
title:  |
        | Legislature Size and Welfare: Evidence from Brazil
author:
date: \today
abstract: "How does legislature size impact public service provision? Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood. In this paper, we use a formal model to show that increasing legislature size improves public goods provision. We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it. We test this theory by exploiting sharp discontinuities in city council size in Brazil. We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures. To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008. This paper has implications for the design of representative institutions."
abstractspacing: double
keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
jelcodes: H41; H80; I31; I38
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

Third, our article also contributes to a growing literature on municipal partisan politics. Most papers in this area estimate the effects of the mayor's party on political outcomes. For instance, \citet{gerber2011mayors} and \citet{de2016mayoral} find differences in governance when comparing Democratic and Republican mayors. Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors. \citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.

Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes. Most papers on legislature size study the trade-off between representation and efficiency \citet{Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}. However, a few new papers explore the effects of legislature size on lawmaking and partisanship \citep{rush2013conclusion, kirkland2014chamber}. For instance, \citet{kirkland2014chamber} shows that in larger legislatures it is harder for politicians to know each other well and collaborate, making them rely more heavily on party cues and committee structures. In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively. \citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda. In this paper, we show that legislature size affects welfare by changing the partisan composition of legislatures.

@@

The design of institutions is crucial for long term welfare \citep{north1989constitutions, buenodemesquita2005logic, acemoglu2012nations}. One particular problem that each polity faces is determination of the size of its legislative bodies. The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{Stigler1976, muzzio1989size}.

The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{taagepera1972size, Stigler1976, muzzio1989size, frederick2008people, rush2013conclusion, jacobs2015explaining}. Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases. This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}. Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures. The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{rush2013conclusion, kirkland2014chamber}. It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}. Balancing these two incentives is crucial for the optimal legislative composition \citep{taagepera1972size, auriol2012optimal}.

However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker? And second, what is the ultimate effect of legislature size on welfare? On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature. It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence. Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}. Of these papers, only \citet{lewis2019legislature} investigated its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} Moreover, \citet{frey2020larger} finds, for the Brazilian case after the 2009 legislature size and salaries constitutional amendment, a null effect in service provision from 2012 to 2016. These findings suggest that the legislature size and welfare nexus need a dedicated theoretical and empirical assessment.

On the other hand, albeit the division of power, in most mayor-council (or presidential) systems, the Executive dominates the service provision. For instance, while the New York Times cited the New York City Mayor Bill De Blasio 2,084 times in 2021, it mentioned the 49 seating city councilors 440 times in the same period. To avoid the COVID crisis when the Executive was in the spotlight, we expanded the search for the past five years. In this new search, Bill De Blasio was mentioned 8,978 while the 49 seating city councilors were mentioned 2,046 times.\footnote{These figures were computed using the Dow Jones Factiva Database in November 2021.} The mayor was cited, on average, over four times more than all the city councilors combined. This Executive dominance has implications for policymaking, as coalitions and affinity with the Executive are going to be crucial for service provision \citep{buenodemesquita2005logic}.

@@

# Results
\label{sec:results}

@@

\begin{table}[!htbp] \centering 
  \caption{Political Effects of Increasing the Number of Legislators} 
  \label{tab:bargain} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
 & \multicolumn{1}{c}{\small{(1)}} 
 & \multicolumn{1}{c}{\small{(2)}} &
 \multicolumn{1}{c}{\small{(3)}} & 
 \multicolumn{1}{c}{\small{(4)}} \\
 & \multicolumn{1}{c}{\small{Mayoral}} & 
 \multicolumn{1}{c}{\small{Num. Politically}} & 
 \multicolumn{1}{c}{\small{Num. Career}} & 
 \multicolumn{1}{c}{\small{Num. Councilor}} \\
 & \multicolumn{1}{c}{\small{Coalition Size}} & 
 \multicolumn{1}{c}{\small{Appointed Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.91$^{*}$ & 104.49$^{*}$ & 71.57 & 2.09 \\ 
  & (0.50) & (61.53) & (218.12) & (4.37) \\ 
    \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
BW Loc Poly & 10.025 & 6.242 & 7.695 & 5.134 \\ 
BW Bias & 15.889 & 10.243 & 11.780 & 8.902 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{Legislature Size and Welfare} 
  \label{tab:outcomes} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
 & \multicolumn{1}{c}{\small{(1)}} 
 & \multicolumn{1}{c}{\small{(2)}} 
 & \multicolumn{1}{c}{\small{(3)}} 
 & \multicolumn{1}{c}{\small{(4)}} \\
 & \multicolumn{1}{c}{\small{Infant}} & 
 \multicolumn{1}{c}{\small{Postneonatal}} &
  \multicolumn{1}{c}{\small{School}} & 
  \multicolumn{1}{c}{\small{Education}} \\ 
   & \multicolumn{1}{c}{\small{Mortality}} & 
 \multicolumn{1}{c}{\small{Mortality}} &
  \multicolumn{1}{c}{\small{Enrollment}} & 
  \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
LATE & -2.01$^{**}$ & -0.90$^{*}$ & 2.52$^{***}$ & -0.03 \\ 
  & (0.79) & (0.48) & (0.80) & (0.13) \\ 
  \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{8597} \\ 
N Right & \multicolumn{1}{c}{1029} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{669} \\ 
Eff N Left & \multicolumn{1}{c}{501} & \multicolumn{1}{c}{324} & \multicolumn{1}{c}{206} & \multicolumn{1}{c}{409} \\ 
Eff N Right & \multicolumn{1}{c}{381} & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{291} \\ 
BW Loc Poly & 7.527 & 7.564 & 5.425 & 9.05 \\ 
BW Bias & 11.95 & 11.01 & 10.58 & 15.107 \\ [1.0ex] 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

## Effects of Legislature Size Changes on Representation, Competitiveness, and Legislative Productivity

>>>>

---
title:  |
        | Legislature Size and Welfare: Evidence from Brazil
author: 
date: \today
abstract: "How does legislature size impact public service provision? Despite the importance of institutional design for democratic governance, the effect of particular legislative features on citizen welfare remains little understood. In this paper, we use a formal model to show that increasing legislature size improves public goods provision. We argue that changes in bargaining costs depend on whether additional legislators share the Executive's party affiliation: More opposition members reduce the Executive's public goods provision, while more government-aligned members increase it. We test this theory by exploiting sharp discontinuities in city council size in Brazil. We show that an additional city councilor has a 91% chance of belonging to the mayoral coalition, and this significantly improves primary school enrollment and infant mortality measures. To explore possible mechanisms, we surveyed former councilors and analyzed 346,553 bills proposed between 2005 and 2008. This paper has implications for the design of representative institutions."
abstractspacing: double
keywords: Legislature Size; Legislative Bargaining; Local Public Goods Provision; Regression Discontinuity Design; Brazil
jelcodes: H41; H80; I31; I38
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

Third, our article also contributes to a growing literature on municipal partisan politics. Most papers in this area estimate the effects of the mayor's party on political outcomes. For instance, \citet{de2016mayoral} and \citet{gerber2011mayors} find differences in governance when comparing Democratic and Republican mayors. Specifically about Brazil, \citet{gouvea2021partisanship} shows that social policy expenditure increase with left-wing mayors. \citet{frey2020larger}, using discontinuities in city council size after the 2009 constitutional amendment that reverted the thresholds we study here, shows that changes in council size lower the support for candidates backed by the municipal mayors. Our paper reinforces the view that partisanship matters locally, even in countries with weak ideological linkage.

Finally, this paper contributes to a growing literature on the causes and effects of legislature sizes. Most papers on legislature size study the trade-off between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, Stigler1976}. However, some recent articles explore the effects of legislature size on lawmaking and partisanship. \citet{kirkland2014chamber} shows that larger legislatures make it harder for politicians to know each other and collaborate, making them rely more heavily on party cues and committee structures. In considering the causes of changes in legislature sizes, \citet{jacobs2015explaining} show that population shifts and economic crises cause enlargement and shrinkage, respectively. \citet{marland2019fewer} questions the economic crises mechanism, showing that political elites shrink legislatures mostly to signal to the public the priority of their austerity agenda. In this article, we show that legislature size affects welfare by changing the partisan composition of legislatures.

@@

The design of institutions is crucial for long term welfare \citep{acemoglu2012nations, buenodemesquita2005logic, north1989constitutions} and democratic consolidation \citep{gandhi2019institutional, lijphart2018institutional}. One particular problem that each polity faces is determination of the size of its legislative bodies. The literature is extensive, and modern attempts to provide a solution to the legislature size problem started as early as in the eighteenth century, with the Federalists versus Anti-Federalists debates \citep{muzzio1989size, Stigler1976}.

The legislature size literature highlights that the number of legislators causes tension between representation and efficiency \citep{frederick2008people, jacobs2015explaining, muzzio1989size, rush2013conclusion, Stigler1976, taagepera1972size}. Larger legislatures improve representation as the election thresholds decrease and the ratio of population-per-politician decreases. This facilitates the electoral success of ethnic and political minorities \citep{allenrepresentation}. Conversely, the improvements in representation are countered by the decline in efficiency in larger legislatures. The enlarged size makes it harder for members to coordinate and collaborate without partisanship and legislative structures \citep{kirkland2014chamber, rush2013conclusion}. It also increases the potential number of veto players, decreasing the policymaking efficiency \citep{tsebelis2002veto}. Balancing these two incentives is crucial for the optimal legislative composition \citep{auriol2012optimal, taagepera1972size}.

However, the legislature size scholarship has overlooked two questions: first, does legislature size matter in contexts where the legislative bodies are not the pivotal decision-maker? And second, what is the ultimate effect of legislature size on welfare? On the one hand, legislature size's effects on welfare represent a significant gap in the political economy literature. It is likely generated by the predominance of the "law of 1/n" scholarship, which emphasized larger legislatures' overspending consequence. Since the seminal paper by \citet{Weingastetal1981}, 30 papers have systematically tested the effects of legislature size on government spending \citep{freire2021legislature}. Of these papers, only \citet{lewis2019legislature} investigates its effects on welfare, showing that larger legislatures have a negative welfare effect.\footnote{\citet{koppel2004public} also shows, using a repeated game where the proposal prerogative rotates in a legislature, that larger legislatures increase the chances of non-cooperative outcomes, lowering public goods provision.} \citet{frey2020larger} analyses the Brazilian case after the 2009 legislature size change and finds a null effect in service provision from 2012 to 2016. These results suggest that the legislature size and welfare nexus needs a dedicated theoretical and empirical assessment.

Despite the division of power, the Executive dominates the debates on public service provision in most mayor-council (or presidential) systems. For instance, while the New York Times cited the New York City Mayor Bill De Blasio 2,084 times in 2021, it mentioned the 49 seating city councilors 440 times in the same period. To avoid the COVID crisis when the Executive was in the spotlight, we expanded the search for the past five years. In this new search, Bill De Blasio was mentioned 8,978 while the 49 seating city councilors were mentioned 2,046 times.\footnote{These figures were computed using the Dow Jones Factiva Database in November 2021.} The mayor was cited, on average, over four times more than all the city councilors combined. This Executive dominance has implications for policymaking, as coalitions and affinity with the Executive are going to be crucial for service provision \citep{buenodemesquita2005logic}.

@@

# Empirical Results
\label{sec:results}

@@

\begin{table}[!htpb] \centering 
  \caption{Political Effects of Increasing the Number of Legislators} 
  \label{tab:bargain} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
 & \multicolumn{1}{c}{\small{(1)}} 
 & \multicolumn{1}{c}{\small{(2)}} &
 \multicolumn{1}{c}{\small{(3)}} & 
 \multicolumn{1}{c}{\small{(4)}} \\
 & \multicolumn{1}{c}{\small{Mayoral}} & 
 \multicolumn{1}{c}{\small{Num. Politically}} & 
 \multicolumn{1}{c}{\small{Num. Career}} & 
 \multicolumn{1}{c}{\small{Num. Councilor}} \\
 & \multicolumn{1}{c}{\small{Coalition Size}} & 
 \multicolumn{1}{c}{\small{Appointed Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Bureaucrats}} & 
 \multicolumn{1}{c}{\small{Assistants}} \\[1ex]  \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
 LATE & 0.91$^{*}$ & 104.49$^{*}$ & 71.57 & 2.09 \\ 
  & (0.50) & (61.53) & (218.12) & (4.37) \\ 
    \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{5179} & \multicolumn{1}{c}{15536} & \multicolumn{1}{c}{15531} & \multicolumn{1}{c}{5179} \\ 
N Right & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{1027} & \multicolumn{1}{c}{344} \\ 
Eff N Left & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{372} & \multicolumn{1}{c}{513} & \multicolumn{1}{c}{99} \\ 
Eff N Right & \multicolumn{1}{c}{162} & \multicolumn{1}{c}{343} & \multicolumn{1}{c}{388} & \multicolumn{1}{c}{101} \\ 
BW Loc Poly & 10.025 & 6.242 & 7.695 & 5.134 \\ 
BW Bias & 15.889 & 10.243 & 11.780 & 8.902 \\ 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

Table \ref{tab:outcomes} shows that increasing the city council by one legislator generates welfare improvement in municipalities. In health care, increasing the legislature size decreases infant mortality in 2.01 deaths per 1,000 children born. This impact is significant in absolute terms and represents an effect of 0.14 in standard deviations. Moreover, postneonatal mortality decreases by 0.90 casualties per 1,000 births, which remains around the 0.14 standard deviations improvement as infant mortality. Infant mortality is a primary outcome for welfare, and it correlates with several other indicators of well-being \citep{world2005health}. The fact that infant mortality improved in the Brazilian case shows that the increased mayor's support mechanism results in large welfare effects. As expected, placebo regressions were statistically insignificant.

In terms of education, with the addition of a city councilor, enrollment in elementary schools increased by 2.58 children on average per school. This represents a change of around 0.20 standard deviations. Besides the influence of the mayoral support, enrollment can also directly impact the councilor's representation: Councilors can pressure the bureaucracy to accommodate a few extra students. With support from the mayor, they can help voters get access to schools, improving the voter's welfare. Education quality remains unchanged, but with more students in the classroom, it could potentially decrease. As expected, the placebo regressions are insignificant.

\begin{table}[!htpb] \centering 
  \caption{Legislature Size and Welfare} 
  \label{tab:outcomes} 
\scalebox{0.9}{
\begin{threeparttable}
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}}l c c c c }
\toprule
 & \multicolumn{1}{c}{\small{(1)}} 
 & \multicolumn{1}{c}{\small{(2)}} 
 & \multicolumn{1}{c}{\small{(3)}} 
 & \multicolumn{1}{c}{\small{(4)}} \\
 & \multicolumn{1}{c}{\small{Infant}} & 
 \multicolumn{1}{c}{\small{Postneonatal}} &
  \multicolumn{1}{c}{\small{School}} & 
  \multicolumn{1}{c}{\small{Education}} \\ 
   & \multicolumn{1}{c}{\small{Mortality}} & 
 \multicolumn{1}{c}{\small{Mortality}} &
  \multicolumn{1}{c}{\small{Enrollment}} & 
  \multicolumn{1}{c}{\small{Quality}} \\[1ex] \cline{2-2} \cline{3-3} \cline{4-4} \cline{5-5}
LATE & -2.01$^{**}$ & -0.90$^{*}$ & 2.52$^{***}$ & -0.03 \\ 
  & (0.79) & (0.48) & (0.80) & (0.13) \\ 
  \hdashline \\[-1.8ex] 
 N Left & \multicolumn{1}{c}{12299} & \multicolumn{1}{c}{5441} & \multicolumn{1}{c}{10156} & \multicolumn{1}{c}{8597} \\ 
N Right & \multicolumn{1}{c}{1029} & \multicolumn{1}{c}{672} & \multicolumn{1}{c}{686} & \multicolumn{1}{c}{669} \\ 
Eff N Left & \multicolumn{1}{c}{501} & \multicolumn{1}{c}{324} & \multicolumn{1}{c}{206} & \multicolumn{1}{c}{409} \\ 
Eff N Right & \multicolumn{1}{c}{381} & \multicolumn{1}{c}{244} & \multicolumn{1}{c}{208} & \multicolumn{1}{c}{291} \\ 
BW Loc Poly & 7.527 & 7.564 & 5.425 & 9.05 \\ 
BW Bias & 11.95 & 11.01 & 10.58 & 15.107 \\ [1.0ex] 
\bottomrule
\end{tabularx}
\begin{tablenotes}
\small
\item \textbf{Note:} $^{***}$p $<$ .01; $^{**}$p $<$ .05; $^{*}$p $<$ .1. RD local linear estimates using \citet{CCT2014} optimal bandwidth quadratic selection and triangular kernel. Robust standard errors, clustered at the municipal level, in parentheses. Controls: population; GDP per capita; number of seats in 2000; year; and dummy for northeast region. \textit{N Left} and \textit{N Right} represent the total number of observations on the left and right sides of the thresholds (untreated). \textit{Eff N Left} and \textit{Eff N Right} are the number of cases within the bandwidth. \textit{BW Loc Poly} is the Bandwidth used to compute the Local Average Treatment Effect (LATE). \textit{BW Bias} is the Bandwidth used to compute the standard errors.
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

## Robustness to Alternative Mechanisms
